% subsection or section?
% move something to appendix
To gain some intuition for eigenvalue spectra, the spectrum of the 2-species food web is investigated analytically. The only feasible food web is that of one producer and one species consuming the producer. The eigenvalues of the 2-species community matrix are
\begin{equation}
    \lambda_{\pm} = -\frac{\alpha_2}{2\beta\eta}\pm \sqrt{\frac{\alpha_2^2}{(2\beta\eta)^2}\left(1 + 2\beta\eta \right) + \left(\alpha_1 - 1 \right)\alpha_2}.
    \label{eq:eig_2}
\end{equation}
Here, $\eta$ and $\beta$ denote $\eta_{21}$ and $\beta_{21}$. Since the steady states in a feasible food web are positive by definition, one obtains that a feasible 2-species food web will always be stable (See Appendix \ref{A:analytical}for details).

The food web will have purely real eigenvalues if
\begin{equation}
    \beta\eta \leq \gamma + \sqrt{\gamma^2 + \gamma}, \:\:\:\:\:\:\:\: \gamma = \frac{\alpha_2}{1-\alpha_1}
\end{equation}
(See Appendix \ref{A:analytical}for details). The food web has real eigenvalues if $\beta\eta$ is in the same range of feasible $\beta\eta$-values as $\alpha_2$ is in the range of feasible $\alpha_2$-values. The feasible range of the latter is limited by $\alpha_1$, which is already present in the food web. In other words a weak interaction strength requires a low consumer decay rate, and vice versa. The decay rate of the producer determines what is a high decay rate for the consumer. 

% need to explain the role of the eigenvalues better before saying this.
%In terms of oscillations, this means that disturbance will only cause damped oscillations if the consumer is strong compared to its resource. The scenario of weak $\beta\eta$ and $\alpha_2$ would be unfeasible. 

The larger food webs rapidly become too complicated to solve analytically.
%, not only because they are polynomials of high degree, but also because of the increasing number of feasible configurations.
However, the results from the 2-species food web roughly generalizes to couples of consumers and resources in larger food web. [elaborate/explain this better!]
